\thispagestyle{empty}
\section*{Abstrakt}
\subsection*{English}
The main goal of this bachelor thesis is the analysis of the most recent attacks on web sites and web applications. In the theoretical part of this thesis chosen attacks have been thoroughly investigated and compared and the methods of prevention have been proposed. These methods cover wide range of possible attacts both with and without frameworks.

The practical part has been focused on development of the penetration testing tool for detection of one of the most dangerous security risk - SQL Injection. The suggested tool uses parameters that are automatically changeable to be fitted for the certain web site or application. The changes in the web site or web application are recorded and compared in order to detect potential security issues.

The tool have been evaluated with existing tools. Unfortunately, there has been found no similar tool available for free with a direct detection function for SQL Injection. Therefore the most similar freeware tools trying to test this security threat have been used for the comparison.

\subsection*{Česky}
Hlavním cílem této bakalářské práce je analýza nejčastějších typů útoků na webové stránky a aplikace. V teoretické části jsou důkladně analyzovány vybrané útoky a jsou ukázány metody prevence s i bez použití frameworků.

Praktická část byla zaměřena na vývoj nástroje pro penetrační testování určeného k detekci jednoho z nejnebezpečnějších bezpečnostních rizik - SQL injection. Navržený nástroj využívá změny parametrů a vyhodnocení změn obsahu na stránce před a po úpravě.

Nástroj byl porovnán s existujícími nástroji a byly analyzovány výsledky. Bohužel zde bylo zjištěno, že neexistuje volně dostupný nástroj, který by nabízel shodnou funkcionalitu. Proto byly v testu použity nástroje požadovaných vlastností.
